On Devon Allen's Disqualification at the 2022 World Track and Field Championships

### 2023-07-26 Manuscript/manuscript.tex
added table
Not compiling correctly

The p value from the two group comparison for 2019 and 2022 was 0.001464.  This 
value is for a one-sided test and show that the mean reaction time on average in
2019 was larger (slower) than the mean reaction time in 2022 for athletes who 
competed in both championships at an $\alpha$ level of 0.01. This provides good
evidence that on average, the reaction times from the 2019 and 2022 World 
Championships are significantly different.  
\jy{elaborate on the inprepretation; what we have rejected;}

@@

It is worth noting that in the semifinals of the 2022 World Track and
Field Championships, Allen's reaction time was 0.101 which is only 0.001 above
the legal limit. What this suggests is that Allen may have strong reflexes
and be able to react extremely well to the sound of the gun. It seems unlikely 
that Allen would be able to correctly predict the gun with such precision two 
times in a row, which is the exact reason that the 0.1 second reaction time 
disqualification barrier was imposed in the first place. Thus having a quick 
reaction time repeatedly may indicate skill rather than luck. Devon Allen is
an exceptional athlete, as evidenced by his football career at the University of
Oregon and making it onto the Philadelphia Eagles practice squad in 2022
\citep{hurley2022eagles}.  \citet{komi2009iaaf}'s paper showed that athletes are
capable of reacting in less than 0.1 seconds, and if this is the case, it is not
unreasonable to conclude that an outstanding athlete like Allen is capable of
reacting below the 0.1 second barrier.

>>>>

\begin{table}
  \centering
  \caption{}
  \begin{tabular}{c c c c c} 
   \toprule
   Comparison & $exact = True$ & $exact \neq True$ & Sample size & Clusters/Athletes \\ 
   \midrule
   2019 vs 2022 & $2.9\cdot10^{-3}$ & $2.3\cdot10{-2}$ & 65 & 15 \\ 
   International & $2.2\cdot10^{-16}$ & $3.1\cdot10^{-4}$ & 61 & 15 \\
   \bottomrule
  \end{tabular}
  \label{tab:Clusrankresults}
\end{table}
The p value from the two group comparison for 2019 and 2022 was 0.001464.  This 
value is for a one-sided test and show that the mean reaction time on average in
2019 was larger (slower) than the mean reaction time in 2022 for athletes who 
competed in both championships at an $\alpha$ level of 0.01. This provides good
evidence that on average, the reaction times from the 2019 and 2022 World 
Championships are significantly different.  
\jy{elaborate on the inprepretation; what we have rejected;}

@@

It is worth noting that in the semifinals of the 2022 World Track and
Field Championships, Allen's reaction time was 0.101 which is only 0.001 above
the legal limit. What this suggests is that Allen may have strong reflexes
and be able to react extremely well to the sound of the gun. It seems unlikely 
that Allen would be able to correctly predict the gun with such precision two 
times in a row, which is the exact reason that the 0.1 second reaction time 
disqualification barrier was imposed in the first place. Thus having a quick 
reaction time repeatedly may indicate skill rather than luck. Devon Allen is
an exceptional athlete, as evidenced by his football career outside of running.  
\citet{komi2009iaaf}'s paper showed that athletes are
capable of reacting in less than 0.1 seconds, and if this is the case, it is not
unreasonable to conclude that an outstanding athlete like Allen is capable of
reacting below the 0.1 second barrier.
